Survival Analysis of Questions Posted on the iFixit Answers forum

### 2018-03-16 article/manuscript.Rnw
file renaming, edit keywords, change colon to divisor in Table 2

\begin{keyword}
cox regression \sep response time \sep survival analysis \sep survival probabilty \sep Q\&A forum 
\end{keyword}

@@

%===================================================================================================
%===================================================================================================

@@

  Of 8,025 questions in the full data, \Sexpr{scales::comma(nrow(x))} were in English (97\% of the full data). Of those questions, \Sexpr{scales::comma(answered)} (\Sexpr{percentans}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{scales::comma(longest)} hours (\Sexpr{scales::comma(longest_d)} days). Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.

@@

Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{mean_d} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{med} hours.

@@

% Splines Square root transformation of the average tag frequency
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
  & 0\textbf{*} & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & 4\textbf{*} & 65910.81 \\ 
  & 3 & 65914.98 \\ 
  \hline
  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
  & 0 & 65918.06 \\ 
  & 5\textbf{*} & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks : text length}}$}
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & 3\textbf{*} & 65881.93 \\ 
  \hline
  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
  & 0 & 65862.83 \\ 
  & 5\textbf{*} & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
\end{tabular}
\caption{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
\label{table:2}
\end{table}

@@

% --------------------------------------------------------------------------------------------------
\subsection{Posted questions}

% answered question id = 397414
% unanswered question id = 399971

@@

% ------------------------------------------------------------------------------------------------

@@

% ------------------------------------------------------------------------

@@

\bibliographystyle{elsarticle-num-names}
\bibliography{questions}

>>>>

\begin{keyword}
Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
\end{keyword}

@@

@@

  Of 8,025 questions in the full data, \Sexpr{scales::comma(nrow(x))} were in English (97\% of the full data). Of those questions, \Sexpr{scales::comma(answered)} (\Sexpr{percentans}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{scales::comma(longest)} hours (\Sexpr{scales::comma(longest_d)} days). Figure 1 shows the distribution of response times for all questions analyzed.

@@

Figure 2 shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{mean_d} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{med} hours.

@@

% Splines Square root transformation of the average tag frequency
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{4}{5 cm}{$\sqrt{\textnormal{average tag frequency}}$} 
  & 0\textbf{*} & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{4}{5 cm}{$\log\left({\textnormal{average tag length} + 1}\right)$}
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & 4\textbf{*} & 65910.81 \\ 
  & 3 & 65914.98 \\ 
  \hline
  \multirow{4}{5 cm}{$\log\left({\textnormal{device length} + 1}\right)$}
  & 0 & 65918.06 \\ 
  & 5\textbf{*} & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{4}{5 cm}{$\sqrt{\textnormal{line breaks / text length}}$}
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & 3\textbf{*} & 65881.93 \\ 
  \hline
  \multirow{4}{5cm}{$\log\left({\textnormal{text length}}\right)$} 
  & 0 & 65862.83 \\ 
  & 5\textbf{*} & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
\end{tabular}
\caption{The model with the lowest AIC was used to determine the optimal k number of splines for each continuous predictor.} 
\label{table:2}
\end{table}

@@

\subsection{Posted questions}

@@

@@

@@

\bibliographystyle{elsarticle-num-names}
\bibliography{references}

### 2018-03-16 article/manuscript.tex
file renaming, edit keywords, change colon to divisor in Table 2

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, 4,951 (63.8\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159 hours (90 days). Figure \ref{fig:1} shows the distribution of response times for all questions analyzed.

Figure \ref{fig:2} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.2 hours.

>>>>

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, 4,951 (63.8\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159 hours (90 days). Figure 1 shows the distribution of response times for all questions analyzed.

Figure 2 shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer soon after it is posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 776 hours, or 32.3 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.2 hours.
